Place of death in NRS COVID-19 deaths: data processing for analysis

### 2021-11-08 covid_nrs_place_of_death_data.Rmd
added a .csv of locations coded as 'other'

>>>>

## Number & proportion of deaths in `Other` location

```{r}
annual_deaths_coded_as_other_place_hb <-
  proportions_of_deaths_by_place_by_geography %>% 
  filter(geography=="hb" & place_of_death == "Other") %>% 
  mutate(num_prop = paste0(format(number_of_deaths, big.mark = ","), " (", scales::percent(proportion_of_total, accuracy = 0.01),")")) %>%
  select(year, place_of_death, ref_area, num_prop) %>% 
  pivot_wider(names_from = year, values_from = num_prop)

annual_deaths_coded_as_other_place_hb %>% write_csv(file = paste0(dir_outputs,"/annual_deaths_coded_as_other_place_hb.csv"))
```
